Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
addressed more todos

In particular, we analyzed contributions in the 
context of continuous integration, using the technical factors found in
some\todo{First: don't use the word some basically ever.  Second: I'm not sure
  what it means to analyze technical factors found in social attributes.  Maybe rephrase?} of the social attributes provided in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.
Overall, our study investigates how well different technical and social factors predict
contribution quality.\todo{One sentence summary of results}  This information can help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.

\textbf{Related work:}
Similar studies have shown the relationship between different\todo{which?
  Social, technical?  Both?} attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
  a habit of saying something like ``...performed a very relevant study where
  they...'' in describing previous work.  This is needlessly wordy.  You can
  write the exact same sentence, more or less (I changed ``determine'' to
  ``show'', ``find'' might also work) without that clause} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor towards acceptance of a pull 
\todo{I think you mean something like ``in predicting acceptance'', not
  ``towards''; do they argue causality?}
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects and how this attributes\todo{wrong word (as in, this is a noun as
  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} study the relationship between the area of the 
source code being modified by the developer initiating a pull request 
and the acceptance rate of these changes is highly correlated.\todo{The
  preceding sentence is not grammatical.  Please fix.} Also existence of 
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.\todo{the
  previous sentence is not a sentence.} Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated to\todo{wrong word} the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

Our study shows that social factors are an important aspect of build success but
these factors alone do not fully predict if a contribution will be successfully 
integrated into the project. We also show
that core team members are more likely to achieve build success than non-core
team members and a developer with followers is more likely to pass the
continuous integration build.\todo{This paragraph doesn't really belong in the
  related work; I might move it above, near where I have a todo asking for a
  summary of results.}

@@

\paragraph{Technical Factors:} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: lines of code changed by this commit.
\item Files added: files added by this commit.
\item Files modified: files modified by this commit.
\item Tests added: tests added by this commit.
\item Tests deleted: tests deleted by this commit.
\item Source files: files in project at the time of the commit.
\item Source loc: lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

@@

\begin{itemize}
\item Repositories: the repositories the developer has access to. This 
includes repositories the developer owns, repositories the developer contributes
to, and repositories for which the developer has organizational membership access.
\footnote{https://developer.github.com/v3/repos/}
\todo{Is this a count, or what?}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}

>>>>

In particular, we analyzed contributions in the 
context of continuous integration, using the technical factors found in
some\todo{First: don't use the word some basically ever.  Second: I'm not sure
  what it means to analyze technical factors found in social attributes.  Maybe rephrase?} of the social attributes provided in the challenge
corpus~\cite{msr17challenge}, and the social factors found on a developer's
GitHub profile.  We used the technical factors to estimate the complexity of the
commit, and the social factors to estimate the developer's experience.
Overall, our study investigates how well different technical and social factors predict
contribution quality. This information can help core team members prioritize project
contributions, and will also provide a further understand of quality enforcement
in the software development process.

Our study shows that social factors are an important aspect of build success but
these factors alone do not fully predict if a contribution will be successfully 
integrated into the project. We also show
that core team members are more likely to achieve build success than non-core
team members and a developer with followers is more likely to pass the
continuous integration build.

\textbf{Related work:}
Similar studies have shown the relationship between different\todo{which?
  Social, technical?  Both?} attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} \todo{Read and delete this comment: one of you has
  a habit of saying something like ``...performed a very relevant study where
  they...'' in describing previous work.  This is needlessly wordy.  You can
  write the exact same sentence, more or less (I changed ``determine'' to
  ``show'', ``find'' might also work) without that clause} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor towards acceptance of a pull 
\todo{I think you mean something like ``in predicting acceptance'', not
  ``towards''; do they argue causality?}
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects and how this attributes\todo{wrong word (as in, this is a noun as
  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

@@

\paragraph{Technical Factors:} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: a count of the lines of code changed by this commit.
\item Files added: a count of the files added by this commit.
\item Files modified: a count of the files modified by this commit.
\item Tests added: a count of the tests added by this commit.
\item Tests deleted: a count of the tests deleted by this commit.
\item Source files: a count of the files in project at the time of the commit.
\item Source loc: a count of the lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

@@

\begin{itemize}
\item Repositories: a count of the repositories the developer has access to. This 
includes repositories the developer owns, repositories the developer contributes
to, and repositories for which the developer has organizational membership access.
\footnote{https://developer.github.com/v3/repos/}
\item Stars: a count of the projects the developer has stared. Starring a project
to shows approval of the repository and creates  a bookmark for later 
access.\footnote{https://help.github.com/articles/about-stars/}
\item Followers: number of developers that follow the author. 
\item Following: number of developers that the author follows 
\item Contributions in the last year: number of contributions made by the author in the last year.
\end{itemize}
